---
title: "extracting average depth data from sonar transects"
author: "MKAUFMAN"
date: "April 22, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## setup
```{r message=FALSE}

library(htmlwidgets)
library(plotly)
library(rgdal)
library(data.table)
```

## import a sonar log from csv (this must be created with the python library sllib ahead of time)

```{r message=FALSE}
#enter the time between initializing the sonar log file name and the start of actual logging. should be about 30 seconds
sonartimeoffsetseconds<-30


sonarfilename='Sonar_2022-08-02_08.48.55B.csv'
rawlog=read.csv(file = sonarfilename,sep=',') 

sonaryear=as.numeric(substr(sonarfilename,7,10))
sonarmonth=as.numeric(substr(sonarfilename,12,13))
sonarday=as.numeric(substr(sonarfilename,15,16))
sonarhour=as.numeric(substr(sonarfilename,18,19))
sonarminute=as.numeric(substr(sonarfilename,21,22))
sonarsecond=as.numeric(substr(sonarfilename,24,25))

sonarstart=substr(sonarfilename,7,25)

sonarstart<-as.POSIXct(strptime(sonarstart, "%Y-%m-%d_%H.%M.%S"))
sonarstart=sonarstart+sonartimeoffsetseconds


#set coordinate system
cord.dec = SpatialPoints(cbind(rawlog$longitude, rawlog$latitude), proj4string=CRS("+proj=longlat"))

#convert to meters (UTM zone 10 north)
cord.UTM <- spTransform(cord.dec, CRS("+init=epsg:32610"))

log=rawlog
log$UTMx=cord.UTM$coords.x1
log$UTMy=cord.UTM$coords.x2
log=log[which(log$framesize==3216),]

#average depth
superroughmeandepthm<-mean(log$water_depth_m)

#create date/time object from start time (from file name), time offset, and elapsed milliseconds
log <- log[order(log$time1),]
log$elapsec<-log$time1/1000
log$sonartime<-sonarstart+log$elapsec

```

## import a hobo depth file (this must be pre-processed in HOBOWARE, including the barometric compensation data assistant. It should have a depth (m) column by the time you are trying to import it here)
```{r message=FALSE}

rawhobo=read.csv(file = '21440089.csv',sep=',',skip=1) 
colnames(rawhobo)<-c("read","datetimePST","AbsPresskPa","TempC","hoboDepthM")
rawhobo$datetimePST<-paste(substr(rawhobo$datetimePST,0,6),"20",substr(rawhobo$datetimePST,7,20),sep="")

rawhobo$datetimePST2<-as.POSIXct(strptime(rawhobo$datetimePST, "%m/%d/%Y %H:%M:%S"))
hobodata<-rawhobo

```
##clean data
```{r}
#get minimum sonar reading
mindepth=min(log$water_depth_m)
#count min
#sum(log$water_depth_m == mindepth)
#remove all minimum entries, as these are "below minimum depth" readings from the sonar
log$water_depth_m[log$water_depth_m == mindepth] <- NA

#remove all very-small hobo depth readings
hobodata$hoboDepthM[hobodata$hoboDepthM<0.1]<-NA
```

##merge hobo data to sonar data
```{r}
setDT(log)
log[, time := sonartime]
setkey(log, time)

setDT(hobodata)
hobodata[, time := datetimePST2]
setkey(hobodata, time)

alldata <- hobodata[log, roll = "nearest"]


```

##subset to a more manageble frequency and plot
```{r}
numpoints<-250
spacing<-round(length(log[,1])/numpoints)
i<-1
alldata_subset<-alldata[1:(i+spacing)==(i+spacing),]
#alldata_subset<-alldata

fig <- plot_ly(type = 'scatter', mode = 'markers',marker=list(
    color=alldata_subset$water_depth_m,
    cmin = 0,
    cmax = 7,
    colorbar=list(
      title='Colorbar'),
    colorscale='Viridis',
    reversescale=TRUE
  )) 
fig <- fig %>%
  add_trace(
    x = alldata_subset$UTMx, 
    y = alldata_subset$UTMy,
    hovertext = alldata_subset$water_depth_m
   
  )

fig

htmlwidgets::saveWidget(partial_bundle(fig), "C:/Users/kauf093/OneDrive - PNNL/Spatial Study 2022/10_Sonar/01_RawData/2022-08-02/S36/sonar.html")

fig <- plot_ly(type = 'scatter', mode = 'markers',marker=list(
    color=alldata_subset$hoboDepthM,
    cmin = 0,
    cmax = 7,
    colorbar=list(
      title='Colorbar'),
    colorscale='Viridis',
    reversescale=TRUE
  )) 
fig <- fig %>%
  add_trace(
    x = alldata_subset$UTMx, 
    y = alldata_subset$UTMy,
    hovertext = alldata_subset$hoboDepthM
   
  )

fig
htmlwidgets::saveWidget(partial_bundle(fig), "C:/Users/kauf093/OneDrive - PNNL/Spatial Study 2022/10_Sonar/01_RawData/2022-08-02/S36/hobo.html")
```

